\documentstyle{article}
\begin{document}
CALL FOR PAPERS
TPDP 2015
First workshop on the Theory and Practice of Differential Privacy
18th April 2015, London, UK
Affiliated to ETAPS
http://tpdp.computing.dundee.ac.uk

Differential privacy is a promising approach to the privacy-preserving
release of data: it offers a strong guaranteed bound on the increase
in harm that a user incurs as a result of participating in a
differentially private data analysis. 

Researchers in differential privacy come from several area of computer
science as algorithms, programming languages, security, databases,
machine learning, as well as from several areas of statistics and data
analysis. The workshop is intended to be an occasion for researchers
from these different research areas to discuss the recent developments
in the theory and practice of differential privacy.

##Submissions##

The overall goal of TPDP is to stimulate the discussion on the
relevance of differentially private data analyses in practice. For
this reason, we seek contributions from different research areas of
computer science and statistics.

Authors are invited to submit a short abstract (4-5 pages maximum) of
their work by January 23, 2015. Abstracts must be written in English
and be submitted as a single PDF file at the EasyChair page for TPDP:
https://easychair.org/conferences/?conf=tpdp2015

Submissions will be judged on originality, relevance, interest and
clarity. Submission should describe novel works or works that have
already appeared elsewhere but that can stimulate the discussion
between the different communities. Accepted abstracts will
be presented at the workshop.

The workshop will not have formal proceedings, but we plan to have a
special issue of the Journal of Privacy and Confidentiality devoted to
TPDP. Authors presenting valuable contributions at the workshop will
be invited to submit a journal version of their work right after the
workshops.

Submissions of abstracts by PC members are allowed and encouraged.

##Important Dates##

January 23, 2015 - Abstract Submission
February 13, 2015 - Notification
April 18, 2015 - Workshop

May 15, 2015 Deadline for journal special issue


##Topics##

Specific topics of interest for the workshop include (but are not limited to):

theory of differential privacy,
verification techniques for differential privacy,
programming languages for differential privacy,
models for differential privacy,
trade-offs between privacy protection and analytic utility,
differential privacy and surveys,
relaxations of the differential privacy definition,
differential privacy vs other privacy notions and methods,
differential privacy and accuracy,
practical differential privacy,
implementations for differential privacy,
differential privacy and security,
applications of differential privacy.

##Invited Speakers##

To be confirmed

##Program Committee##

Gilles Barthe - IMDEA Software
Konstantinos Chatzikokolakis - CNRS and LIX, Ecole Polytechnique
Kamalika Chaudhuri - UC San Diego
Graham Cormode - University of Warwick
George Danezis - University College London
Marco Gaboardi - University of Dundee
Matteo Maffei - CISPA, Saarland University
Catuscia Palamidessi - INRIA and LIX, Ecole Polytechnique
Benjamin C. Pierce - University of Pennsylvania
Aaron Roth - University of Pennsylvania
David Sands - Chalmers University of Technology
Chris Skinner - London School of Economics
Adam Smith - Pennsylvania State University
Carmela Troncoso - Gradiant
Salil Vadhan - Harvard University
\end{document}